InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

Another importance to notice is the usage of different evaluators. In both cases, text and image we had one evaluator respectively which could not be fooled no matter what. These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
If those were the only detectors we would have had, the result would look like there could nothing be done to fool an AI detector.

>>>>

Another noticeable result is in the usage of different evaluators. In both cases, text and image, we had one evaluator respectively which could not be fooled with any method. These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
If those were the only detectors we would have had, the result would look like there could nothing be done to fool an AI detector.
